---
title: "Select a car based on Horse power and miles per gallon!"
author: "Gianluca Kikidis"
date: "29.06.2021"
output:
  slidy_presentation: default
  html_document:
    number_sections: yes
    toc: yes
  ioslides_presentation: default
mode: selfcontained
job: Reproducible Pitch Presentation
highlighter: highlight.js
widgets: bootstrap
---

## Reproducible Pitch

I created a Shiny application in order to select cars from the mtcars data set in R
based on their Horse Powers. With this application, a plot is shown in which you can
see the miles per gallon a car makes with a specific horsepower.


```{r, echo = FALSE, eval = TRUE}
library(ggplot2)
library(shinycustomloader)
library(shiny)
```

## shinyUI part

In this part i create the structure of the app, including what has to be displayed etc.

```{r, echo = TRUE, eval = FALSE}
shinyUI(fluidPage(
    titlePanel("Car selection based on horsepower and miles per gallon using Shiny and ggplot"),
    sidebarLayout(
        sidebarPanel(
            checkboxInput("show_xlab", "Show/Hide X Axis Label", TRUE),
            checkboxInput("show_ylab", "Show/Hide Y Axis Label", TRUE),
            sliderInput("hp","Select minimum Horse Power",52,335,52)
        ),
        mainPanel(
            h3("Select a car based on horse power and miles per gallon"),
                plotOutput("plot1") )
            )
)
)
```

## Then i create the shinyServer part, including codes and comands for the app:

```{r, echo = TRUE, eval = FALSE}
shinyServer(function(input, output) {
    filtered_data <- reactive({
        sub <- subset(
            mtcars,
            hp >= input$hp[1]
        )
        sub
    })
    output$plot1 <- renderPlot({
        sub <- filtered_data()
        xlab <- ifelse(input$show_xlab, "Horse Power", "")
        ylab <- ifelse(input$show_xlab, "Miles Per Gallon", "")
ggplot(sub, aes_string(y = sub$mpg, x= sub$hp)) +
            labs(x = xlab, y = ylab) +
                geom_point(size = sub$wt) +
                ggtitle("Thicker points equal heavier cars, while thinner points equal lighter cars")
        })
    })
```

## Discussion

And this is how i created my first little app. It might not be too interesting, but
i am still glad i made it and also i had to limit myself a bit because of my computer
not working very well. 


Thank you :)